MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
add mg7 for shotgun as a future development -- paper
See https://github.com/ohnosequences/metagenomica/issues/26#issuecomment-139857648

>>>>

\subsubsection{Shotgun metagenomics}\label{shotgun-metagenomics}

It is certainly possible to adapt MG7 to work with shotgun metagenomics
data. Simply changing the reference database to include whole genome
sequence data could yield interesting results. This could also be
refined by restricting reference sequences according to all sort of
criteria, like biological function or taxonomy. Bio4j would be an
invaluable tool here, thanks to its ability to express express complex
predicates on sequences using all the information linked with them (GO
annotations, UniProt data, NCBI taxonomy, etc).
